Supplementary Materials

### 2022-12-27 manuscript/supplementary.tex
some updates

Under the background selection model, the diversity in window $b$ is $\pi(b,
\Psi) = \bar{B}(b, \Psi) \pi_0$. Here, $\bar{B}(b | \Psi)$ is the predicted
reduction in diversity due to BGS in window $b$, given background selection
parameters $\Psi$. In practice, we pre-calculate $\bar{B}(b | \Psi)$ at fixed
sites across the genome, and take the average of the fixed sites $B$ values
within a widow.

>>>>

Under the background selection model, the diversity in window $b$ is $\pi(b,
\Psi) = \bar{B}(b, \Psi) \pi_0$. Here, $\bar{B}(b | \Psi)$ is the predicted
reduction in diversity due to BGS in window $b$, given background selection
parameters $\Psi$. In practice, we pre-calculate $\bar{B}(x | \Psi)$ at fixed
sites $x$ across the genome, and take the average of the fixed sites $B$ values
within widow $b$ for the average $\bar{B}(b | \Psi)$.

There are two ways to parameterize background selection models. Both models use
a fixed $q$-grid of selection coefficients ranging $s \in \{10^{-6}, 10^{-5},
10^{-4}, 10^{-3}, 10^{-2}, 10^{-1}\}$ (here, $q=6$) and interpolate over a grid
of mutation rates. First, for the \emph{free-mutation} parameterization, each
annotation feature class has a free mutation rate parameter for each of these
selection coefficients. That is, the distribution of fitness effect (DFE) is
implied by the total mutation rate across selection coefficients for an
annotation class.  We can normalize by the total mutation rate estimate to get
the estimated DFE, giving us the DFE weight for annotation class $k$ and
selection coefficient with index $i$,

\begin{align}
  \widehat{w}_{i,k} = \frac{\widehat{\mu}_{i,k}}{\sum_i \widehat{\mu}_{i,k}}.
\end{align}

With this parameterization, there are $1 + K \times q$ for $\pi_0$ and the free
DFE parameters, where $K$ is the number of annotation features. The MLE
optimization for this approach is unconstrained, though $\pi_0$ is bounded to
be within $10^{-5} \le \pi_0 \le 10^{-1}$.

\begin{align}
  W = \begin{bmatrix}
    \mu_{10^{-6},\text{CDS}} & \mu_{10^{-6},\text{UTR}} & w_{10^{-6},\text{phastcons}} \\
    \mu_{10^{-5},\text{CDS}} & \mu_{10^{-5},\text{UTR}} & w_{10^{-5},\text{phastcons}} \\
    \vdots & \vdots & \vdots \\
    \mu_{10^{-1},\text{CDS}} & \mu_{10^{-1},\text{UTR}} & w_{10^{-1},\text{phastcons}} \\
  \end{bmatrix}
\end{align}

The second parametrization is the \emph{simplex} parametrization, which has a
single mutation rate across all features, and the DFE is parameterized by a
matrix $W$

which has $2
+ K \times (q-1)$ free parameters.
